---
title: "Examples with Local Data"
description: >
  A Quarto article scaffold for examples that rely on data available in a
  local research environment.
vignette: >
  %\VignetteIndexEntry{Examples with Local Data}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: "#>"
---

This article is a placeholder for examples that should be rendered locally
before publishing the pkgdown site. That workflow is useful when an example
depends on licensed data, local database access, or files that should not be
stored in the public GitHub repository.

The package's included data can be used in public examples without additional
setup:

```{r}
library(farr)
library(dplyr, warn.conflicts = FALSE)

comp |>
  select(gvkey, fyear, big_n, ta, roa) |>
  slice_head(n = 5)
```

For examples that depend on private inputs, keep the source code in this
article and render the site locally with:

```{r}
#| eval: false
pkgdown::build_site()
```

The rendered HTML under `docs/` can then be published without committing the
underlying private data.
